Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/splitting.tex
Fix typo.

Rather than attempt global optimization of the outputs of splitting,
we instead introduce world \bbonep\ and use the type system to
statically prove terms contain no second stage computations.  In these
situations, splitting is trivial---splitting $\pure e$ terms yields a
unit resumer.

>>>>

Rather than attempt global optimization of the outputs of splitting,
we instead introduce world \bbonep\ and use the type system to
statically prove certain terms contain no second stage computations.
In these situations, splitting is trivial---splitting $\pure e$ terms
yields a unit resumer.
